Paper 1 Notebook

### 2023-12-01 minos/outcomes/paper_1_notebook.Rmd
adding progress bar to MICE

  mice_set <- futuremice(data = mice.data[, imp_columns], #method=method,
                   m = n_iter, minit = max_iter,
                   remove.collinear=T, progressor = progressor)
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}

>>>>

  mice_set <- with_progress(futuremice(data = mice.data[, mice_columns], #method=method,
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T, 
                   progressor = progressr::handlers("progress")))
  saveRDS(mice_set, "data/transitions/MICE_set.rds")
}
